Paper 1 Notebook

### 2023-12-01 minos/outcomes/paper_1_notebook.Rmd
finish mice script

mice.data$ethnicity <- factor(mice.data$ethnicity)
mice.data$S7_labour_state <- factor(mice.data$S7_labour_state)
mice.data$region <- factor(mice.data$region)
mice.data$heating <- factor(mice.data$heating)
mice.data$job_sec <- factor(mice.data$job_sec)
mice.data$education_state <- factor(mice.data$education_state)
mice.data$sex <- factor(mice.data$sex)
#mice.data$smoker <- factor(mice.data$smoker)
mice.data$behind_on_bills <- factor(mice.data$behind_on_bills)
mice.data$ghq_depression <- factor(mice.data$ghq_depression)
mice.data$ghq_happiness <- factor(mice.data$ghq_happiness)
mice.data$clinical_depression <- factor(mice.data$clinical_depression)
mice.data$scsf1 <- factor(mice.data$scsf1)
mice.data$health_limits_social <- factor(mice.data$ghq_depression)
mice.data$housing_tenure <- factor(mice.data$housing_tenure)
mice.data$urban <- factor(mice.data$urban)
mice.data$marital_status <- factor(mice.data$marital_status)

>>>>

mice.data$ethnicity <- factor(mice.data$ethnicity)
mice.data$S7_labour_state <- factor(mice.data$S7_labour_state)
mice.data$region <- factor(mice.data$region)
mice.data$loneliness <- factor(mice.data$loneliness)
#mice.data$heating <- factor(mice.data$heating)
#mice.data$job_sec <- factor(mice.data$job_sec)
#mice.data$education_state <- factor(mice.data$education_state)
#mice.data$sex <- factor(mice.data$sex)
#mice.data$smoker <- factor(mice.data$smoker)
#mice.data$behind_on_bills <- factor(mice.data$behind_on_bills)
#mice.data$ghq_depression <- factor(mice.data$ghq_depression)
#mice.data$ghq_happiness <- factor(mice.data$ghq_happiness)
#mice.data$clinical_depression <- factor(mice.data$clinical_depression)
#mice.data$scsf1 <- factor(mice.data$scsf1)
#mice.data$health_limits_social <- factor(mice.data$ghq_depression)
#mice.data$housing_tenure <- factor(mice.data$housing_tenure)
#mice.data$urban <- factor(mice.data$urban)
#mice.data$marital_status <- factor(mice.data$marital_status)
